SeisAcoustic

### 2019-06-28 docs/latex/Acoustic_FWI/paper.tex
frequency gradient

>>>>

\subsubsection{Connection between first order and second order Acoustic wave equation}
The first order acoustic wave equation is expressed  as
\begin{equation}
\begin{split}
 \frac{\partial v_z}{\partial t} &=  b \frac{\partial p}{\partial z}  \\
 \frac{\partial v_x}{\partial t} &=  b \frac{\partial p}{\partial x}  \\
\frac{\partial p}{\partial t} &= k \left(\frac{\partial v_z}{\partial z} + \frac{\partial v_x}{\partial x} \right) + f(t)
\end{split}
\label{in1}
\end{equation}
To derive the second order expression, we need to apply the time derivative to both side of the third equation expressed in equation \ref{in1}, we can get
\begin{equation}
\begin{split}
\frac{\partial^2 p}{\partial t^2} &= \frac{\partial}{\partial t}\left( k \left(\frac{\partial v_z}{\partial z} + \frac{\partial v_x}{\partial x} \right) \right) + \frac{\partial f(t)}{\partial t} \\
&=  k \left(\frac{\partial}{\partial z}\frac{\partial v_z}{\partial t} + \frac{\partial}{\partial x}\frac{\partial v_x}{\partial t} \right)  + \frac{\partial f(t)}{\partial t} 
\end{split}
\label{in2}
\end{equation}
As the model parameter $k$ is independent of time variable $t$ and exchange the order of 
partial derivative along time and spatial direction, next we are going to the expression in the first two equations of equation \ref{in1} to change the variable $\frac{\partial v_z}{\partial t}$ and  $\frac{\partial v_x}{\partial t}$, we can get
\begin{equation}
\frac{\partial^2 p}{\partial t^2} = k \left(  \frac{\partial}{\partial z} (b \frac{\partial p}{\partial z}) + \frac{\partial}{\partial x} (b \frac{\partial p}{\partial x})  \right) + \frac{\partial f(t)}{\partial t}
\label{in3}
\end{equation}
we can move the first term in the right hand side of equation \ref{in3} to the left hand side, dived by $k$, we get
\begin{equation}
\frac{1}{k}\frac{\partial^2 p}{\partial t^2} -  \left(  \frac{\partial}{\partial z} (b \frac{\partial p}{\partial z}) + \frac{\partial}{\partial x} (b \frac{\partial p}{\partial x})  \right) = \frac{1}{k}\frac{\partial f(t)}{\partial t}
\label{in4}
\end{equation}
The next step is to perform Fourier transform to frequency domain, we can get
\begin{equation}
\frac{-w^2}{k} p -  \left(  \frac{\partial}{\partial z} (b \frac{\partial p}{\partial z}) + \frac{\partial}{\partial x} (b \frac{\partial p}{\partial x})  \right) = \frac{iw f(w)}{k}
\label{in5}
\end{equation}
